### 2010-11-15 docs/tex/mimicry.tex
Paraphrasing fixed.

According to Muller \cite{muller1879} Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution. In Muller's view, this convergence or sharing of the warning signal reduces the predation load on each species. The entry of a naive young predator into the population has usually been considered the primary cause of learning predation.  In such a case, both Mullerian species should benefit from mutual advertising. In any event, a mutant that more strongly resembles a warningly colored species is expected to be more likely to survive predation than one that changes in the opposite direction. Predators of warningly colored species are encouraged to generalize; that is, it is to their benefit to recognize similar patterns as signaling unpalatability. Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance confer some protection. Note that Mullerian mimicry is not deceptive since it is to the predator's advantage to be able to recognize all deterrent and trauma-inducing species. The mimicry does not have to be close enough to cause misidentification on the part of the predator, merely close enough to remind it of a past experience with similar prey.  Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise. Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.75]{images/BatesMimButter}
	\caption{Perhaps one of the most well-known examples of mimicry, the viceroy butterfly (top) appears very similar to the noxious tasting monarch butterfly (bottom). Although it was for a long time purported to be an example of Batesian mimicry, it has recently been discovered that the viceroy is actually just as unpalatable as the monarch, making this a case of Mullerian mimicry. \cite{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
	\label{fig:mullerian-butterfly}
\end{figure}

@@

\paragraph{Punctuated Equilibrium}
Punctuated equilibrium is a theory in evolutionary biology which proposes that most sexually reproducing species will experience little evolutionary change for most of their geological history, remaining in an extended state called \textit{stasis}. When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis. Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another. Thus, ``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}.

>>>>

According to Huheey \cite{huheey1988} ``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution \cite{muller1879}." In Muller's view, predation load on each species are reduced when their warning signals are shared or converged. Naive young predators create the most impact in learning predation as they start their life with no knowledge or experience over the prey species. For cases like these, all unpalatable species should benefit from mutual advertising. If mutation gives opportunity for a single unpalatable prey to resemble a warningly colored species, it is expected to be more likely to survive predation than if the change was in opposite direction. Predators surviving on warningly colored species need to generalize; meaning if similar patterns signal unpalatability, predators recognition rate becomes much higher. Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance provides some protection.

It is worth observing the fact that Mullerian mimicry is not deception, as it is to the predator's advantage to be able to recognize all deterrent and noxious species. Preys resemblance does not have to be close enough to cause misidentification on the part of the predator, but merely similar enough to remind it of a bitter past experience with similar prey. As Huheey continues ``Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise. Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian. "

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.75]{images/BatesMimButter}
	\caption{A very well-known examples of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom). It was considered for a long time that this is an ideal example of Batesian mimicry. But recently Brower discovered that the viceroy is actually just as noxious as the monarch, making this a case of Mullerian mimicry. \cite{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
	\label{fig:mullerian-butterfly}
\end{figure}

@@

\paragraph{Punctuated Equilibrium}
In evolutionary biology, punctuated equilibrium is the theory which proposes that most sexually reproducing species will remain in an extended state called \textit{stasis} while experiencing little evolutionary change for most of their geological history. When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis. Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another. Thus, ``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}.
